---
title: "Baby Names by Sex and Mother Ethnic Group"
author: "Chi Ting Low https://github.com/chitinglow"
output: html_document
runtime: shiny
---

```{r, warning=FALSE, message=FALSE,echo=FALSE}
library(jsonlite)
library(lubridate)
library(ggplot2)
library(dplyr)
library(shiny)
library(DT)
library(plotly)


json_file <- 'https://datahub.io/JohnSnowLabs/baby-names-by-sex-and-mother-ethnic-group/datapackage.json'
json_data <- fromJSON(paste(readLines(json_file), collapse = ""))

# print all tabular data(if exists any)
for (i in 1:length(json_data$resources$datahub$type)) {
  if (json_data$resources$datahub$type[i] == 'derived/csv') {
    path_to_file = json_data$resources$path[i]
    Birth <- read.csv(url(path_to_file))
  }
}

Birth_data <- cbind(Birth, day = day(Birth$Birth_Year), month = month(Birth$Birth_Year), year = year(Birth$Birth_Year))

Birth_year <- select(Birth_data, year, Gender, Ethnic_Group, Count)

Birth_year$Ethnic_Group <- recode(Birth_year$Ethnic_Group, `ASIAN AND PACI` = 'Asian and Pacific Islander',`ASIAN AND PACIFIC ISLANDER` = 'Asian and Pacific Islander', `BLACK NON HISPANIC` = 'Black Non Hispanic'  , `BLACK NON HISP` = 'Black Non Hispanic', `WHITE NON HISP` = 'White Non Hispanic', `WHITE NON HISPANIC` = 'White Non Hispanic', HISPANIC = 'Hispanic')

renderDataTable({
  Birth
})


```

# Introduction

The following dataset is the gathered from [Data Hub](https://datahub.io/JohnSnowLabs/baby-names-by-sex-and-mother-ethnic-group). There are 6 columns and 13962 rows in the dataset. For the purpose of the analysis, only *Birth_data*, *year*, *Gender*, *Ethnic_Group* and *Count* was selected. The data contains the birth of the baby from 2011-11-08 to 2014-11-08. The count of the baby birth is collected every 11-08 and it represented frequency the name of the baby named from diffrent gender and ethnic group. The analysis shows that there
were total 7139 female and 6823 male were born from 2011-2014. Among that, there were 2310 Asian and Pacific Islander, 2627 Black Non Hispanic, 4254 Hispanic and 4771 White Non Hispanic. 


```{r, warning=FALSE, message=FALSE,echo=FALSE}

renderPlotly({
  
  ggplotly(ggplot(Birth_year, aes(x = year, y = Count, fill = Gender)) + 
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(title = 'Number of Birth by Gender from 2011 to 2014', x = 'Year', y = 'Count') + 
  theme_bw() +
  scale_fill_brewer(palette = "Set1"))
})

renderPlotly({
  
  ggplotly(ggplot(Birth_year, aes(x = year, y = Count, fill = Ethnic_Group)) + 
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(title = 'Number of Birth by Ethnic Group from 2011 to 2014', x = 'Year', y = 'Count') + 
  guides(fill = guide_legend(title = "Ethnic Group")) +
  scale_fill_brewer(palette = "Set1"))
})


renderPlotly({
  
  ggplotly(ggplot(Birth_year, aes(x = Ethnic_Group, y = Count, fill = Gender)) + 
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(title = 'Number of Birth by Gender and Ethinic Group from 2011 to 2014', x = 'Ethnic Group', y = 'Count') + 
  theme_bw() +
  scale_fill_brewer(palette = "Set1"))
})

```

As presented in the bar chart, it shows that more male is born but graduatly decrease from 2011 to 2014, it was opposited compared to female. As comparison, there is a decreasing of hispanic baby born from 2011 to 2014. However, in total hispanic has the most baby born from 2011 to 2014. 